Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-05 manuscript_results.Rmd
update

# Plot the difference using ggplot2
ggplot(summed_data_all, aes(x = Julian_date, y = (Difference)*100, color = Week)) +
#  geom_line(size = 1) +        # Line plot
  geom_point(size = 2) +       # Points on the line
#  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1) +  # Reference line at 0
  theme_minimal() +
  labs(
    title = "Percentage of WIS difference across all states AUTO_AVG_LB compared to baseline",
    x = "Julian Date",
    y = "Difference (1 - AUTO_AR_NoLg / AUTO_AVG)"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

# Plot the difference using ggplot2
ggplot(summed_data_all, aes(x = Julian_date, y = (Difference)*100, color = Week)) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Mean percentage of WIS difference across all states",
    subtitle =  "AUTO_AVG_LB compared to baseline",
    x = "Julian Date",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),  # adjust if necessary
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  )
```
